environmental_data_preperation

### 2018-10-25 src/environmental_data_preperation.Rmd
GEBCO_AEA

```{r}
library(ncdf4)
gebco <- nc_open("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
gebco
library(marmap)
bat <-readGEBCO.bathy("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
summary(bat)
```

@@

might be easier just to work form a TIF though...

First project the tiff to equal area
```{r}
library(raster)
geb <- "../data/env/gebco.tif"
mask1 <- "../data/env/aea.tif" #just for canada pc as file isn't loaded
aea <- raster(mask1)
gebr <- brick(geb)
gebr
aea
geb
geb_aea <- projectRaster(geb, aea) 
```

```{r GEBCO raster extraction}
library(rgdal)
library(sp)
gebco_coordinates(data_aea) <- c("decimalLongitude", "decimalLatitude") 
nafo_zones <- readOGR(dsn=path.expand("../data/bio/nafo_zones"), layer = "nafo_zones_wgs84") #this loads the shapefile
proj4string(adddata) <- proj4string(nafo_zones) #tells R that the occurrence data is the same projection as the shapefile
adddata$nafo_zone <- over(adddata, nafo_zones)$ZONE #ZONE is where the zone data is held in teh shapefiles' attributes
head(adddata) #just to check it worked
```

>>>>

```{r}
library(ncdf4)
library(marmap)
bat <-readGEBCO.bathy("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
summary(bat)
```

@@

```{r}
write.csv(data_aea,"../output/bio/data_aea_cell_amo_nao_bins_btmdepth.csv", row.names = FALSE)
```

note that you will still need to project the bathymetric layer to aea to do the mapping on...

I THINK THIS WILL BE SOLVED ON MY REAL PC - SAM DEAL WITH THIS!

```{r}
library(raster)
mask1 <- "../data/env/aea.tif" #just for canada pc as file isn't loaded
aea <- raster(mask1)
gebco <- raster("../data/env/GEBCO_2014_2D_-70.0_34.0_-43.0_70.0.nc")
gebco
prj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
gebco_aea <- projectRaster(gebco, prj)  
gebco_aea
```

```{r}
plot(gebco_aea)
```
